---
title: "stats101B_HW1"
author: "Ryan Chu"
date: "2024-04-05"
output: pdf_document
---

```{r, include = FALSE}
library(ggplot2)
library(ggfortify)
library(dplyr)
```
#Q1

## 1.

```{r, include = FALSE}
library(readr)
meth_data <- read_csv("Downloads/Stats101B_Dataset - Sheet1.csv")
```

```{r}
meth_data
```


## 2.

```{r}
s1 <- meth_data$Score1
s2 <- meth_data$Score2
t.test(s1, s2, paired = TRUE, alternative = "two.sided")

ggplot(meth_data, aes(x=Score2-Score1)) + geom_histogram(binwidth=1, color = "black", fill = "blue")
``` 
Ho: True mean difference is equal to 0
Ha: True mean difference is not equal to 0

Since the p-value(0.4201) is greater than 0.05, we fail to reject the null hypothesis.

## 3.
```{r}
ggplot(meth_data, aes(x=Sex, y=Score2)) + geom_boxplot()
```
## 4.

```{r}
aggregate(data = meth_data, Score2~Sex, var)

var.test(data=meth_data, Score2~Sex)
```
From the var test we can conclude that there isn't a difference between the Female and Male variances.

## 5.

```{r}
t.test(Score2~Sex, data = meth_data, var.equal = TRUE)
```

Since our p-value is greater than 0.05, we fail to reject the null that the true difference in means between Females and Males is greater than 0.

# Q2

## a.

H0 = mean breaking strength = 150
HA = mean breaking strength <= 150

## b.

```{r}
y <- c(145, 153, 150, 147)

(mean(y) - 150)/(2/2)

pnorm(-1.25, lower.tail = TRUE)
```

Since the p-value is greater than 0.05, we fail to reject the null hypothesis.

## c.

0.1056498

## d. 

```{r}
mean(y) + c(-1, 1) * (1.96 * 2)/2

mean(y)
```
CI = 146.79 to 150.71

(mean of y is within this confidence interval, so makes sense that we failed to reject the null)

# Q3

## a.

```{r}
values <-  c(65, 81, 57, 66, 82, 82, 67, 59, 75, 70, 64, 71, 83, 59, 65, 56, 69, 74, 82, 79)
type <- c("type1", "type1", "type1", "type1", "type1", "type1", "type1", "type1", "type1", "type1", "type2", "type2", "type2", "type2", "type2", "type2", "type2", "type2", "type2", "type2")

q3_df <- data.frame(values, type)

aggregate(values~type, data = q3_df, var)

var.test(values~type, data = q3_df, alternative = "two.sided")
```

Since the p value is greater than 0.05, we fail to reject the null that the two variances are equal. (So we can say the varainces are equal)

## b.

```{r}
t.test(values~type, data = q3_df, var.equal = TRUE)
```
Since our p value is greater than 0.05, we fail to reject the null that different between the means is equal to 0.

# c.

```{r}
library(ggplot2)

ggplot(q3_df, aes(type, values)) + geom_boxplot()
```
Looking at the boxplots, Type 1 and Type 2 seem to violate the normality assumption

# Q4

```{r}
anova_table <- matrix(ncol = 5, nrow = 3)

colnames(anova_table) <- c('DF', 'SS', 'MS', 'F', 'P')
rownames(anova_table) <- c('Factor', 'Error', 'Total')

anova_table[1, 1] <- 3
anova_table[1, 2] <- 36.15
anova_table[3, 1] <- 19
anova_table[3, 2] <- 196.04

anova_table[2, 1] <- anova_table[3, 1] - anova_table[1, 1]
anova_table[2, 2] <- anova_table[3, 2] - anova_table[1, 2]

anova_table[1, 3] <- anova_table[1, 2]/anova_table[1, 1]
anova_table[2, 3] <- anova_table[2, 2]/anova_table[2, 1]

anova_table[1, 4] <- anova_table[1, 3]/anova_table[2, 3]

anova_table[1, 5] <- pf(anova_table[1, 4], 3, 16, lower.tail=FALSE)

anova_table
```

